M.Sc. Proposal: \\ \bigskip Computational Electrokinetics

### 2013-01-03 notes/thesis-latex-template/thesis.tex
Update thesis.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Solver Design}
Let $\cO : \R^N \rightarrow \R^N $ be an nonlinear operator.
In order to solve the equation $\cO(\bx) = \bzero$, Newton's method is applied, 
given an initial solution $\bx_0$.
Each step requires the computation of the residual vector, $\br = \cO(\bx)$, and
the gradient matrix of the operator, $\bG = \bnabla \cO(\bx)$, 
given the current solution $\bx$.

@@

@@

\section{Future Work}
Future work may include replacing the full Newton step by an iterative linear solver
(e.g. using preconditioned Krylov subspace methods \cite{saad2003book} or
Multigrid), allowing finer grids to be used.
In addition, the framework may be used for automatic construction of Newton solvers 
for other nonlinear PDE systems, for example -- for particle with different surface 
properties, or different particle shape.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Solver Design}
Let $\cO : \R^N \rightarrow \R^N $ be an nonlinear operator.
In order to solve the equation $\cO(\bx) = \bzero$, Newton's method is applied, 
given an initial solution $\bx_0$.
Each step requires the computation of the residual vector, $\br = \cO(\bx)$, 
the gradient matrix of the operator, $\bG = \bnabla \cO(\bx)$
(given the current solution $\bx$)
and the solution of sparse linear system $\bG \Delta \bx = -\br$.

@@

MATLAB direct solver is applied to solve the sparse linear system for each Newton step,
using the backslash operator. 
The library used for solving the linear system is UMFPACK 5.0 \cite{davis2004umfpack}
(Unsymmetric MultiFrontal Sparse LU Factorization Package),
as reported by MATLAB function call, \verb|spparms('spumoni', 2)|.

@@

\section{Future Work}
Future work may include optimizing the direct sparse linear solver 
to use the ordering data from previous calls,
or replacing the full Newton step by an iterative linear solver
(e.g. using preconditioned Krylov subspace methods \cite{saad2003book} or
Multigrid), allowing finer grids to be used.
In addition, the framework may be used for automatic construction of Newton solvers 
for other nonlinear PDE systems, for example -- for particle with different surface 
properties, or different particle shape.
